Queue Aware Precoder Design for Space Frequency Resource Allocation

### 2014-07-14 Report/problem_formulation.tex
updated kkt,wsrm,admm,primal

The problem defined in \eqref{q_gen_sum} ignores the second order term arising from the Lyapunov drift minimization objective by the limiting it to a constant value. Eq. \eqref{eqn-4.2} provides similar expression when the exponent is set to be \me{q=2} as
\begin{equation}\label{pf-1}
\underset{t_k}{\text{minimize}} \, \sum_k \, v_k^2 = \underset{t_k}{\text{minimize}} \, \sum_k \, Q_k^2 - 2 \, Q_k t_k + t_k^2.
\end{equation}
It is evident that \eqref{pf-1} is equivalent to \eqref{backpreassure} when we ignore the second order terms from \eqref{pf-1}. Limiting \me{t_k^2} by a constant value, imposes the additional rate constraint \eqref{eqn-3.1.4} in the \ac{Q-WSRM} formulation to avoid the resource wastage in the form of over allocation. In the current queue deviation formulation, the explicit rate constraint is not needed, since it is handled by the objective function itself. In contrast to the \ac{WSRM} formulation, the \ac{JSFRA} and the \ac{Q-WSRM} problems include the sub-channels jointly to achive an efficient allocation by identifying the optimal space-frequency resource for each user in the system. The queue deviation objective provides an alternate and a more efficient way to perform the resource allocation as compared to the \eqref{q_gen_sum} approach.

Before proceeding further, we note that the constraint in \eqref{eqn-4.2} is handled implicitly by the definition of the \me{\ell_q} in the objective of \eqref{eqn-3}. As a proof, suppose that \me{t_k>Q_k} for a certain \me{k} at optimum, i.e., \me{-{v}_k=t_k-Q_k>0}. Then there exists \me{\delta_k>0} such that \me{-{v}^{\prime}_k=t^{\prime}_k-Q_k<-{v}_k} where \me{t^{\prime}_k=t_k-\delta_k}. Since \me{\|\tilde{\mbf{v}}\|_q=\| |\tilde{\mbf{v}}| \|_q=\||-\tilde{\mbf{v}}|\|_q}, this means that the newly created vector \me{\mbf{t}^{\prime}} achieves a smaller objective which contradicts with the fact that an optimal solution has been obtained. We comment on the choice of  the \me{\ell_q} on the objective as below \cite{berry2004cross,qps_cioffi}.
\begin{itemize}
\item With \me{q = 1}, the objective results in greedy allocation \textit{i.e}, emptying the queue of users with good channel condition before considering the users with worse channel conditions. As a special case, it is easy to see that \eqref{eqn-3} reduces to the \ac{WSRM} problem \eqref{gen_sum} when the queue size is large enough for all users.
\item With \me{q = 2}, the objective prioritizes users with higher number of queued packets before considering the users with a smaller number of backlogged packets. For example, it could be more ideal for the delay limited scenario when the packet arrival rates of the users are similar, since the backlogged packets is proportional to the delay in the transmission following the Little's law \cite{neely2010stochastic}.
\item With \(q = \infty \), the objective minimizes the maximum number of queued packets among users with the current transmission, thereby providing queue fairness by allocating the resources proportional to the number of backlogged packets.
\end{itemize}

>>>>

The problem defined in \eqref{q_gen_sum} ignores the second order term arising from the Lyapunov drift minimization objective by the limiting it to a constant value. Eq. \eqref{eqn-4.2} provides similar expression when the exponent is set to be \me{\ell_{q=2}} as
\begin{equation}\label{pf-1}
\underset{t_k}{\text{minimize}} \, \sum_k \, v_k^2 = \underset{t_k}{\text{minimize}} \, \sum_k \, Q_k^2 - 2 \, Q_k t_k + t_k^2.
\end{equation}
It is evident that \eqref{pf-1} is equivalent to \eqref{backpreassure} when we ignore the second order terms from \eqref{pf-1}. Limiting \me{t_k^2} by a constant value, imposes the additional rate constraint \eqref{eqn-3.1.4} in the \ac{Q-WSRM} formulation to avoid the resource wastage in the form of over allocation. In the current queue deviation formulation, the explicit rate constraint is not needed, since it is handled by the objective function itself. In contrast to the \ac{WSRM} formulation, the \ac{JSFRA} and the \ac{Q-WSRM} problems include the sub-channels jointly to achive an efficient allocation by identifying the optimal space-frequency resource for each user in the system. The queue deviation objective provides an alternate and a more efficient way to perform the resource allocation as compared to the \eqref{q_gen_sum} approach.

Before proceeding further, we note that the constraint in \eqref{eqn-4.2} is handled implicitly by the definition of the \me{\ell_q} in the objective of \eqref{eqn-3}. As a proof, suppose that \me{t_k>Q_k} for a certain \me{k} at optimum, i.e., \me{-{v}_k=t_k-Q_k>0}. Then there exists \me{\delta_k>0} such that \me{-{v}^{\prime}_k=t^{\prime}_k-Q_k<-{v}_k} where \me{t^{\prime}_k=t_k-\delta_k}. Since \me{\|\tilde{\mbf{v}}\|_q=\| |\tilde{\mbf{v}}| \|_q=\||-\tilde{\mbf{v}}|\|_q}, this means that the newly created vector \me{\mbf{t}^{\prime}} achieves a smaller objective which contradicts with the fact that an optimal solution has been obtained. The choice of the norm \me{\ell_q} used in the objective function \cite{berry2004cross,qps_cioffi} alters the priorities for the queue deviation function as
\begin{itemize}
\item With \me{\ell_{q = 1}}, the objective results in greedy allocation \textit{i.e}, emptying the queue of users with good channel condition before considering the users with worse channel conditions. As a special case, it is easy to see that \eqref{eqn-3} reduces to the \ac{WSRM} problem \eqref{gen_sum} when the queue size is large enough for all users.
\item With \me{\ell_{q = 2}}, the objective prioritizes users with higher number of queued packets before considering the users with a smaller number of backlogged packets. For example, it could be more ideal for the delay limited scenario when the packet arrival rates of the users are similar, since the backlogged packets is proportional to the delay in the transmission following the Little's law \cite{neely2010stochastic}.
\item With \(\ell_{q = \infty} \), the objective minimizes the maximum number of queued packets among users with the current transmission, thereby providing queue fairness by allocating the resources proportional to the number of backlogged packets.
\end{itemize}

### 2014-07-14 Report/sub_channel_wsrm.tex
updated kkt,wsrm,admm,primal

The complexity involved in the \ac{JSFRA} scheme scales up significantly based on the sub-channel over which the decision has to be made. Not only the complexity, but also the convergence speed depends on the size  and the number of decision variables involved in the optimization problem. In order to reduce the complexity involved in the \ac{JSFRA} scheme, we provide an alternative sub-optimal solution, where the precoders are designed over each sub-channel independently in a sequential manner by taking the remaining number of queued bits into consideration. It provides an alternative way to the parallel sub-channel wise precoder update using the decomposition techniques discussed in \cite{palomar2006tutorial,boyd2011distributed}.

The proposed \acf{QM} \ac{SRA} scheme decouples the fixing the power across each sub-channel to a constant value as compared to the global power constraint defined by \eqref{eqn-4.3}. In contrast to the decomposition based approach for sub-channel wise resource allocation, this method requires the update on the number of queued bits before each sub-channel level optimization. In this approach, the number of queued bits are updated by the difference between the total number of queued bits during the current slot and the total number of bits that are guaranteed by the earlier sub-channel wise allocations in the same slot as
\begin{equation}
Q_{k,n} = \max{\Big \lbrace Q_k - \sum_{j = 1}^{n-1} \, \sum_{l = 1}^{L} \, t_{l,k,j} ,0 \Big \rbrace }, \; \forall \; k \in \mathcal{U}
\label{eqn-weight}
\end{equation}
where \me{Q_{k,n}} is the total number of queued bits used in the optimization problem carried out for the sub-channel \me{n}. In the expression \eqref{eqn-weight}, \me{Q_k} denotes the total number of queued bits waiting to be transmitted for the user \me{k} during the current slot and \me{t_{l,k,j}} is the rate or guaranteed bits allocated over the sub-channel \me{j}. The current scheme is very sensitive to the order in which the sub-channels are selected for the optimization problem.

>>>>

The complexity involved in the \ac{JSFRA} scheme scales significantly with the increase in the number of sub-channels considered in the formulation. In addition to the increased complexity, the rate of convergence to the optimal precoders also degrades due to its dependency on the problem size. In order to mitigate this, we provide an alternative sub-optimal solution, in which the precoders are designed over each sub-channel independently in a sequential manner by taking the reamining number of queued bits in the formulation. It provides a sub-optimal solution to the optimal way of distributing the sub-channel wise precoder design via primal/dual decomposition methods discussed in \cite{palomar2006tutorial,boyd2011distributed}.

The proposed \acf{QM} \ac{SRA} scheme decouples the problem by fixing the power across each sub-channel to a constant value as compared to the global power constraint defined by \eqref{eqn-4.3}. In contrast to the decomposition based approach for the sub-channel wise resource allocation, where the primal/dual variables are exchanged, this method requires the update on the number of queued bits before each sub-channel level optimization. The number of queued bits for each user are updated by the difference between the total number of queued bits during the current slot to the total number of bits that are guaranteed by the earlier sub-channel wise allocations in the same slot as
\begin{equation}
Q_{k,n} = \max{\Big \lbrace Q_k - \sum_{j = 1}^{n-1} \, \sum_{l = 1}^{L} \, t_{l,k,j} ,0 \Big \rbrace }, \; \forall \; k \in \mathcal{U}
\label{eqn-weight}
\end{equation}
where \me{Q_{k,n}} is the total number of queued bits used in the optimization problem carried out for the sub-channel \me{n}. In the expression \eqref{eqn-weight}, \me{Q_k} denotes the total number of queued bits waiting to be transmitted for the user \me{k} during the current slot and \me{t_{l,k,j}} is the rate or guaranteed bits allocated over the sub-channel \me{j}. The current scheme is very sensitive to the order in which the sub-channels are selected for the optimization problem.

### 2014-07-14 Report/wsrm_formulation.tex
updated kkt,wsrm,admm,primal

In this approach, we present an iterative algorithm to solve \eqref{eqn-3} locally based on the idea of alternating optimization and successive convex approximation. Using \eqref{eq:SINR}, we can reformulate the problem defined in \eqref{eqn-3} as
\begin{IEEEeqnarray}{RCL}\label{eqn-6}
\underset{\substack{\gamma_{l,k,n},\mvec{m}{l,k,n},\\\beta_{l,k,n},\mvec{w}{l,k,n}}}{\text{minimize}} & \quad & \|  \tilde{\mbf{v}}  \|_q \label{eqn-obj} \IEEEyessubnumber \\
\text{subject to}& \quad &\gamma_{l,k,n} \leq \dfrac{\mvec{w}{l,k,n}^\herm \mvec{H}{l,k,n} \mvec{m}{l,k,n}}{\beta_{l,k,n}} \triangleq f(\tilde{\mbf{u}}_{l,k,n}),\IEEEyessubnumber \label{eqn-6.2} \\
  & \quad & \beta_{l,k,n} \geq  N_0 + \hspace{-0.75em} \sum_{(j,i) \neq (l,k)} \hspace{-0.75em} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2, \IEEEyessubnumber \label{eqn-6.3} \\
  & \quad &\eqref{eqn-4.3} \IEEEyessubnumber
\end{IEEEeqnarray}
where \me{\beta_{l,k,n}} denotes the total interference seen by the \me{l^\mathrm{th}} stream of the user \me{k} on the \me{n^\mathrm{th}} sub-channel and let \me{\tilde{\mbf{u}}_{l,k,n} \triangleq \{\mvec{w}{l,k,n}^\herm, \mvec{H}{b_k,k,n}, \mvec{m}{l,k,n},\beta_{l,k,n}\}} be the vector which needs to be identified for the optimal allocation. In this formulation, we relaxed the equality constraint in \eqref{eq:SINR} by the inequalities in \eqref{eqn-6.2} and \eqref{eqn-6.3}. However, this step is without loss of optimality leads to the same solution, since the inequalities in \eqref{eqn-6.2} and \eqref{eqn-6.3} are active for an optimal solution, following the same arguments as those in \cite{tran2012fast}. Intuitively, \eqref{eqn-6.2} denotes the \ac{SINR} constraint for \me{\gamma_{l,k,n}}, and \eqref{eqn-6.3} gives an upper bound for the interference seen by the user \me{k \in \mathcal{U}_b}. The problem in \eqref{eqn-6} is known to be NP-hard even for the single antenna case \cite{wmmse_shi,kaleva2013primal}. The reformulation in \eqref{eqn-6} allows a tractable solution as presented below. First, we note that the constraints \eqref{eqn-4.3} are convex with involved variables. Thus, we only need to deal with \eqref{eqn-6.2} and \eqref{eqn-6.3}. Towards this end, we resort to the traditional coordinate descent technique by fixing the transmit beamformers, and find the optimal linear receivers. The optimal linear receiver for the fixed transmit precoders \me{\mbf{M}_{i,n} \, \forall i \in \mc{U}, \, \forall n \in \mc{C}} is obtained by minimizing \eqref{eqn-3} w.r.t the \me{\mbf{w}_{l,k,n}}, and the closed form solution is given by
\begin{IEEEeqnarray}{rCl}\label{eqn-10}
\mvec{w}{l,k,n} &=& \mathbf{R}^{-1}_{l,k,n} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n}, \IEEEyessubnumber \\
\mvec{R}{l,k,n} &=& \displaystyle \sum_{i\in \mc{U}} \sum_{j=1}^L \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \mvec{m}{j,i,n}^\herm \mvec{H}{b_i,k,n}^\herm + \mathbf{I}_{N_R}, \IEEEyessubnumber
\end{IEEEeqnarray}
which is the \ac{MMSE} receive beamformers \cite{christensen2008weighted,wmmse_shi,kaleva2013primal}.

The problem now is to find optimal transmit beamformers for a given set of linear receivers which is a challenging task. We note that for fixed $\mvec{w}{l,k,n}$, \eqref{eqn-6.3} can be written as a \ac{SOC} constraint. Thus, the difficulty is due to the non-convexity in \eqref{eqn-6.2}. To arrive at a tractable formulation, we adopt the \ac{SCA} method to handle \eqref{eqn-6.2} by replacing the original non-convex constraint by the series of convex constraints. Note that the function \me{f(\tilde{\mbf{u}}_{l,k,n})} in \eqref{eqn-6.2} is convex for fixed \me{\mvec{w}{l,k,n}} since it is in fact the ratio between a quadratic form (of \me{\mvec{m}{l,k,n}}) over an affine function (of \me{\beta_{l,k,n}}) \cite{boyd2004convex}. According to the \ac{SCA} method, we relax \eqref{eqn-6.2} to a convex constraint in each iteration of the iterative procedure. Since \me{f(\tilde{\mbf{u}}_{l,k,n})} is convex, a concave approximation of \eqref{eqn-6.2} can be easily found by considering the first order approximation of \me{f(\tilde{\mbf{u}}_{l,k,n})} around the current operation point. For this purpose, let the real and imaginary component of the complex number \me{\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}} be represented by
\begin{subeqnarray} \label{eqn-wsrm-expr}
p_{l,k,n} &\triangleq& \Re \set{{\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}}}, \\
q_{l,k,n} &\triangleq& \Im \set{{\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}}},
\end{subeqnarray}
and hence \me{f(\tilde{\mbf{u}}_{l,k,n})=(p_{l,k,n}^2 + q_{l,k,n}^2)/\beta_{l,k,n}}. Note that \me{p_{l,k,n}} and \me{q_{l,k,n}} are just symbolic notation and not the newly introduced optimization variables. In CVX \cite{grant2008cvx}, for example,  we declare \me{p_{l,k,n}} and \me{q_{l,k,n}} with the `\emph{expression}' qualifier. Suppose that the current value of \me{p_{l,k,n}} and \me{q_{l,k,n}} at a specific iteration are \me{\tilde{p}_{l,k,n}} and \me{\tilde{q}_{l,k,n}}, respectively. Using the first order Taylor approximation around the local point \me{ [ \, \tilde{p}_{l,k,n},\tilde{q}_{l,k,n},\tilde{\beta}_{l,k,n} \, ]^T}, we can approximate \eqref{eqn-6.2} by the following linear inequality constraint
\begin{equation}
\label{eqn-8}
2 \dfrac{\tilde{p}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left ( p_{l,k,n} - \tilde{p}_{l,k,n} \right ) + 2 \dfrac{\tilde{q}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left ( q_{l,k,n} - \tilde{q}_{l,k,n} \right ) + \dfrac{\tilde{p}_{l,k,n}^2 + \tilde{q}^2_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left (1 - \dfrac{\beta_{l,k,n} - \tilde{\beta}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \right ) \geq \gamma_{l,k,n}.
\end{equation}
In summary, for the fixed linear receivers, the \ac{JSFRA} problem to find transmit beamformers is shown by
\begin{IEEEeqnarray}{rCl}\label{eqn-9}
\underset{\substack{\gamma_{l,k,n},p_{l,k,n},q_{l,k,n} \\ \mvec{m}{l,k,n}, \beta_{l,k,n}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}} \|_q \IEEEyessubnumber\label{eqn-9.1a} \\
\text{subject to} & \quad & \beta_{l,k,n} \geq  N_0 + \hspace{-0.75em} \sum_{(j,i) \neq (l,k)} \hspace{-0.75em} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2, \IEEEyessubnumber \label{eqn-9.1c} \\
& \quad&\sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \text{tr} \, (\mvec{M}{k,n} \mvec{M}{k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \label{eqn-9.1d} \\
& \quad & \text{and } \eqref{eqn-8} \IEEEyessubnumber \label{eqn-9.1e}.
\end{IEEEeqnarray}

>>>>

In this approach, we present an iterative algorithm to solve \eqref{eqn-3} locally based on the idea of alternating optimization and successive convex approximation. Using \eqref{eq:SINR}, we can reformulate the problem defined in \eqref{eqn-3} as
\begin{IEEEeqnarray}{RCL}\label{eqn-6}
\underset{\substack{\gamma_{l,k,n},\mvec{m}{l,k,n},\\\beta_{l,k,n},\mvec{w}{l,k,n}}}{\text{minimize}} & \quad & \|  \tilde{\mbf{v}}  \|_q \label{eqn-obj} \IEEEyessubnumber \\
\text{subject to}& \quad &\gamma_{l,k,n} \leq \dfrac{\mvec{w}{l,k,n}^\herm \mvec{H}{l,k,n} \mvec{m}{l,k,n}}{\beta_{l,k,n}} \triangleq f(\tilde{\mbf{u}}_{l,k,n}),\IEEEyessubnumber \label{eqn-6.2} \\
  & \quad & \beta_{l,k,n} \geq  N_0 \|\mvec{w}{l,k,n}\|^2 + \hspace{-0.75em} \sum_{(j,i) \neq (l,k)} \hspace{-0.75em} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2, \IEEEyessubnumber \label{eqn-6.3} \\
  & \quad &\eqref{eqn-4.3} \IEEEyessubnumber
\end{IEEEeqnarray}
where \me{\beta_{l,k,n}} denotes the total interference seen by the \me{l^\mathrm{th}} stream of the user \me{k} on the \me{n^\mathrm{th}} sub-channel and let \me{\tilde{\mbf{u}}_{l,k,n} \triangleq \{\mvec{w}{l,k,n}^\herm, \mvec{H}{b_k,k,n}, \mvec{m}{l,k,n},\beta_{l,k,n}\}} be the vector which needs to be identified for the optimal allocation. In this formulation, we relaxed the equality constraint in \eqref{eq:SINR} by the inequalities in \eqref{eqn-6.2} and \eqref{eqn-6.3}. However, this step is without loss of optimality leads to the same solution, since the inequalities in \eqref{eqn-6.2} and \eqref{eqn-6.3} are active for an optimal solution, following the same arguments as those in \cite{tran2012fast}. Intuitively, \eqref{eqn-6.2} denotes the \ac{SINR} constraint for \me{\gamma_{l,k,n}}, and \eqref{eqn-6.3} gives an upper bound for the interference seen by the user \me{k \in \mathcal{U}_b}. The problem in \eqref{eqn-6} is known to be NP-hard even for the single antenna case \cite{wmmse_shi,kaleva2013primal}. The reformulation in \eqref{eqn-6} allows a tractable solution as presented below. First, we note that the constraints \eqref{eqn-4.3} are convex with involved variables. Thus, we only need to deal with \eqref{eqn-6.2} and \eqref{eqn-6.3}. Towards this end, we resort to the traditional coordinate descent technique by fixing the transmit beamformers, and find the optimal linear receivers. The optimal linear receiver for the fixed transmit precoders \me{\mbf{M}_{i,n} \, \forall i \in \mc{U}, \, \forall n \in \mc{C}} is obtained by minimizing \eqref{eqn-3} w.r.t the \me{\mbf{w}_{l,k,n}}, and the closed form solution is given by
\begin{IEEEeqnarray}{rCl}\label{eqn-10}
\mvec{w}{l,k,n} &=& \mathbf{R}^{-1}_{l,k,n} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n}, \IEEEyessubnumber \\
\mvec{R}{l,k,n} &=& \displaystyle \sum_{i\in \mc{U}} \sum_{j=1}^L \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \mvec{m}{j,i,n}^\herm \mvec{H}{b_i,k,n}^\herm + N_0 \, \mathbf{I}_{N_R}, \IEEEyessubnumber
\end{IEEEeqnarray}
which is the \ac{MMSE} receive beamformers \cite{christensen2008weighted,wmmse_shi,kaleva2013primal}.

The problem now is to find optimal transmit beamformers for a given set of linear receivers which is a challenging task. We note that for fixed $\mvec{w}{l,k,n}$, \eqref{eqn-6.3} can be written as a \ac{SOC} constraint. Thus, the difficulty is due to the non-convexity in \eqref{eqn-6.2}. To arrive at a tractable formulation, we adopt the \ac{SCA} method to handle \eqref{eqn-6.2} by replacing the original non-convex constraint by the series of convex constraints. Note that the function \me{f(\tilde{\mbf{u}}_{l,k,n})} in \eqref{eqn-6.2} is convex for fixed \me{\mvec{w}{l,k,n}} since it is in fact the ratio between a quadratic form (of \me{\mvec{m}{l,k,n}}) over an affine function (of \me{\beta_{l,k,n}}) \cite{boyd2004convex}. According to the \ac{SCA} method, we relax \eqref{eqn-6.2} to a convex constraint in each iteration of the iterative procedure. Since \me{f(\tilde{\mbf{u}}_{l,k,n})} is convex, a concave approximation of \eqref{eqn-6.2} can be easily found by considering the first order approximation of \me{f(\tilde{\mbf{u}}_{l,k,n})} around the current operation point. For this purpose, let the real and imaginary component of the complex number \me{\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}} be represented by
\begin{subeqnarray} \label{eqn-wsrm-expr}
p_{l,k,n} &\triangleq& \Re \set{{\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}}}, \\
q_{l,k,n} &\triangleq& \Im \set{{\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}}},
\end{subeqnarray}
and hence \me{f(\tilde{\mbf{u}}_{l,k,n})=(p_{l,k,n}^2 + q_{l,k,n}^2)/\beta_{l,k,n}}. Note that \me{p_{l,k,n}} and \me{q_{l,k,n}} are just symbolic notation and not the newly introduced optimization variables. In CVX \cite{grant2008cvx}, for example,  we declare \me{p_{l,k,n}} and \me{q_{l,k,n}} with the `\emph{expression}' qualifier. Suppose that the current value of \me{p_{l,k,n}} and \me{q_{l,k,n}} at a specific iteration are \me{\tilde{p}_{l,k,n}} and \me{\tilde{q}_{l,k,n}}, respectively. Using the first order Taylor approximation around the local point \me{ [ \, \tilde{p}_{l,k,n},\tilde{q}_{l,k,n},\tilde{\beta}_{l,k,n} \, ]^T}, we can approximate \eqref{eqn-6.2} by the following linear inequality constraint
\begin{equation}
\label{eqn-8}
2 \dfrac{\tilde{p}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left ( p_{l,k,n} - \tilde{p}_{l,k,n} \right ) + 2 \dfrac{\tilde{q}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left ( q_{l,k,n} - \tilde{q}_{l,k,n} \right ) + \dfrac{\tilde{p}_{l,k,n}^2 + \tilde{q}^2_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left (1 - \dfrac{\beta_{l,k,n} - \tilde{\beta}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \right ) \geq \gamma_{l,k,n}.
\end{equation}
In summary, for the fixed linear receivers, the \ac{JSFRA} problem to find transmit beamformers is shown by
\begin{IEEEeqnarray}{rCl}\label{eqn-9}
\underset{\substack{\gamma_{l,k,n},p_{l,k,n},q_{l,k,n} \\ \mvec{m}{l,k,n}, \beta_{l,k,n}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}} \|_q \IEEEyessubnumber\label{eqn-9.1a} \\
\text{subject to} & \quad & \beta_{l,k,n} \geq  N_0\|\mvec{w}{l,k,n}\|^2 + \hspace{-0.75em} \sum_{(j,i) \neq (l,k)} \hspace{-0.75em} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2, \IEEEyessubnumber \label{eqn-9.1c} \\
& \quad&\sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \text{tr} \, (\mvec{M}{k,n} \mvec{M}{k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \label{eqn-9.1d} \\
& \quad & \text{and } \eqref{eqn-8} \IEEEyessubnumber \label{eqn-9.1e}.
\end{IEEEeqnarray}
